
## Filter Cells

We filter out, by default, cells that have unique gene counts over 2,500 or less than
200 Note that low.thresholds and high.thresholds are used to define a
'gate' -Inf and Inf should be used if you don't want a lower or upper
threshold.  These can be changed from default when first rendering the document.

```{r FilterThreshold}

obj <- FilterCells(object = obj, 
                   subset.names = c("nGene", "percent.mito"), 
                   low.thresholds = c(obj@calc.params$CreateSeuratObject$min.genes, -Inf), 
                   high.thresholds = c(Inf, 0.05))
```


## Normalizing Data

After removing unwanted cells from the dataset, the next step is to normalize the data. By default, we employ a global-scaling normalization method “LogNormalize” that normalizes the gene expression measurements for each cell by the total expression, multiplies this by a scale factor (10,000 by default), and log-transforms the result.

```{r NormalizeData}
obj <- NormalizeData(object = obj, 
                      normalization.method = "LogNormalize", 
                      scale.factor = 10000)
```

## Detection of Variable Genes

Seurat calculates highly variable genes and focuses on these for downstream analysis. FindVariableGenes calculates the average expression and dispersion for each gene, places these genes into bins, and then calculates a z-score for dispersion within each bin. This helps control for the relationship between variability and average expression. This function is unchanged from (Macosko et al.), but new methods for variable gene expression identification are coming soon. We suggest that users set these parameters to mark visual outliers on the dispersion plot, but the exact parameter settings may vary based on the data type, heterogeneity in the sample, and normalization strategy. The parameters here identify ~2,000 variable genes, and represent typical parameter settings for UMI data that is normalized to a total of 1e4 molecules.


```{r DetectVarGenes}
obj <- FindVariableGenes(object = obj, 
                         mean.function = ExpMean, 
                         dispersion.function = LogVMR, 
                         x.low.cutoff = 0.0125, 
                         x.high.cutoff = 3, 
                         y.cutoff = 0.5)

length(x = obj@var.genes)
```


## Scaling Data

Your single cell dataset likely contains ‘uninteresting’ sources of variation. This could include not only technical noise, but batch effects, or even biological sources of variation (cell cycle stage). As suggested in Buettner et al, NBT, 2015, regressing these signals out of the analysis can improve downstream dimensionality reduction and clustering. To mitigate the effect of these signals, Seurat constructs linear models to predict gene expression based on user-defined variables. The scaled z-scored residuals of these models are stored in the scale.data slot, and are used for dimensionality reduction and clustering.

We can regress out cell-cell variation in gene expression driven by batch (if applicable), cell alignment rate (as provided by Drop-seq tools for Drop-seq data), the number of detected molecules, and mitochondrial gene expression. For cycling cells, we can also learn a ‘cell-cycle’ score (see example [HERE]) and regress this out as well. In this simple example here for post-mitotic blood cells, we regress on the number of detected molecules per cell as well as the percentage mitochondrial gene content.

Seurat v2.0 implements this regression as part of the data scaling process. Therefore, the <code>RegressOut</code> function has been deprecated, and replaced with the vars.to.regress argument in <code>ScaleData</code>.

```{r ScaleData}
obj <- ScaleData(object = obj, vars.to.regress = c("nUMI", "percent.mito"))
```
