
## QC and selecting cells for further analysis

While the <code>CreateSeuratObject</code> imposes a basic minimum gene-cutoff, you may want to filter out cells at this stage based on technical or biological parameters. Seurat allows you to easily explore QC metrics and filter cells based on any user-defined criteria. In the example below, we visualize gene and molecule counts, plot their relationship, and exclude cells with a clear outlier number of genes detected as potential multiplets. Of course this is not a guaranteed method to exclude cell doublets, but we include this as an example of filtering user-defined outlier cells. We also filter cells based on the percentage of mitochondrial genes present.

### QC

```{r QCSelection}
# The number of genes and UMIs (nGene and nUMI) are automatically calculated
# for every object by Seurat.  For non-UMI data, nUMI represents the sum of
# the non-normalized values within a cell We calculate the percentage of
# mitochondrial genes here and store it in percent.mito using AddMetaData.
# We use object@raw.data since this represents non-transformed and
# non-log-normalized counts The % of UMI mapping to MT-genes is a common
# scRNA-seq QC metric.  NOTE: You must have the Matrix package loaded to
# calculate the percent.mito values.
mito.genes <- grep(pattern = "^mt-", x = rownames(x = obj@data), value = TRUE)
percent.mito <- Matrix::colSums(obj@raw.data[mito.genes, ])/Matrix::colSums(obj@raw.data)

# AddMetaData adds columns to object@meta.data, and is a great place to
# stash QC stats
obj <- AddMetaData(object = obj, metadata = percent.mito, col.name = "percent.mito")
VlnPlot(object = obj, features.plot = c("nGene", "nUMI", "percent.mito"), nCol = 3)
```

### Gene Plot

```{r GenePlot}
# GenePlot is typically used to visualize gene-gene relationships, but can
# be used for anything calculated by the object, i.e. columns in
# object@meta.data, PC scores etc.  Since there is a rare subset of cells
# with an outlier level of high mitochondrial percentage and also low UMI
# content, we filter these as well
par(mfrow = c(1, 2))
GenePlot(object = obj, gene1 = "nUMI", gene2 = "percent.mito")
GenePlot(object = obj, gene1 = "nUMI", gene2 = "nGene")
```