
## Perform linear dimensional reduction

Next we perform PCA on the scaled data. By default, the genes in <code>object@var.genes</code> are used as input, but can be defined using pc.genes. We have typically found that running dimensionality reduction on highly variable genes can improve performance. However, with UMI data - particularly after regressing out technical variables, we often see that PCA returns similar (albeit slower) results when run on much larger subsets of genes, including the whole transcriptome.

Seurat provides several useful ways of visualizing both cells and genes that define the PCA, including <code>PrintPCA</code>, <code>VizPCA</code>,  <code>PCAPlot</code>, and <code>PCHeatmap</code>

### PrintPCA

```{r RunPCA}
obj <- RunPCA(object = obj, 
              pc.genes = obj@var.genes, 
              do.print = TRUE, 
              pcs.print = 1:5, 
              genes.print = 10)
```

### VizPCA

```{r VizPCA}
VizPCA(object = obj, pcs.use = 1:2)
```

### PCA Plot

```{r PCAPlot}
PCAPlot(object = obj, dim.1 = 1, dim.2 = 2)
```

### Project PCA

ProjectPCA scores each gene in the dataset (including genes not included
in the PCA) based on their correlation with the calculated components.
Though we don't use this further here, it can be used to identify markers
that are strongly correlated with cellular heterogeneity, but may not have
passed through variable gene selection.  The results of the projected PCA
can be explored by setting use.full=T in the functions above

```{r ProjectPCA}
obj <- ProjectPCA(object = obj, do.print = FALSE)
```
